% Code

```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

# Import Data


```{r}
library(knitr)
library(tidyverse)
library(janitor)
fhb_sev <- read_csv("data/dat-sev.csv")

fhb_sev %>%
  tabyl(AI2, n_spray)

# Renaming the treatments 
library(plyr)
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("check-0" = "AACHECK"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Azoxistrobina + Tebuconazole-2" = "AZOX + TEBU 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Piraclostrobina + Metconazole-2" = "PIRA + METC 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Tebuconazole-2" = "TEBU 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Trifloxistrobina + Protioconazole-2" = "TFLX + PROT 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Trifloxistrobina + Tebuconazole-2" = "TFLX + TEBU 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Piraclostrobina + Metconazole-1" = "PIRA + METC 1X"))
detach("package:plyr", unload = TRUE)


# create the log of the FHB index variable
fhb_sev <- fhb_sev %>%
  mutate(log_sev = log(sev))

# create the sampling variance for the log of FHB index
fhb_sev$vi <- with(fhb_sev, V_sev / (n * sev^2))
```

# Cooperative Trials

```{r}
fhb_sev_coop = fhb_sev %>% 
  filter(publication == "Boletim")
```


## covariance structure

Now we will fit models with CS, HCS and UN matrix-covariance structure. We will then compare them with `anova` function to choose among the best model.

```{r}

library(metafor)


mv_sev_HCS <- rma.mv(log_sev, vi,
  mods = ~AI2,
  random = list(~AI2 | factor(trial)),
  struct = "HCS",
  method = "ML",
  data = fhb_sev_coop
)

mv_sev <- rma.mv(log_sev, vi,
  mods = ~AI2,
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_coop
)

mv_sev
```


We can see below that the UN structure is a better model.

```{r}

anova(mv_sev_HCS, mv_sev)
AIC(mv_sev_HCS)
```


## Percent control

Let's obtain the percent control from the estimated ratios.

```{r}

efficacy_sev <- data.frame(cbind(
  (1 - exp(mv_sev$b)) * 100,
  (1 - exp(mv_sev$ci.lb)) * 100,
  (1 - exp(mv_sev$ci.ub)) * 100
))



efficacy_sev
```

## Contrasts

We can set linear contrasts between treatments of interest and get the P-value using the `anova` function.


```{r}
anova(mv_sev, L = rbind(
  c(0, 1, -1, 0, 0, 0),
  c(0, 1, 0, -1, 0, 0),
  c(0, 1, 0, 0, -1, 0),
  c(0, 1, 0, 0, 0, -1),
  c(0, 0, 1, -1, 0, 0),
  c(0, 0, 1, 0, -1, 0),
  c(0, 0, 1, 0, 0, -1),
  c(0, 0, 0, 1, -1, 0),
  c(0, 0, 0, 1, 0, -1),
  c(0, 0, 0, 0, 1, -1)
))
```


## Moderators

### Cultivar 

```{r}
# creating two groups of cultivars (MR, S)
table(fhb_sev_coop$cultivar, fhb_sev_coop$reaction)
nrow(table(fhb_sev_coop$cultivar, fhb_sev_coop$reaction))

# Renaming the reactions 
library(plyr)
fhb_sev_coop$reaction <- revalue(fhb_sev_coop$reaction, c("MS" = "S"))
fhb_sev_coop$reaction <- revalue(fhb_sev_coop$reaction, c("MS/MR" = "MR"))
fhb_sev_coop$reaction <- revalue(fhb_sev_coop$reaction, c("MR/R" = "MR"))
fhb_sev_coop$reaction <- revalue(fhb_sev_coop$reaction, c("MS/S" = "S"))
detach("package:plyr", unload = TRUE)

table(fhb_sev_coop$cultivar, fhb_sev_coop$reaction)
table(fhb_sev_coop$reaction)
table(fhb_sev_coop$AI2, fhb_sev_coop$reaction)


```

```{r}
library(metafor)


mv_reaction <- rma.mv(log_sev, vi,
  mods = ~AI2*reaction,
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_coop
)

mv_reaction


anova(mv_reaction, btt=8:10)
```

### Disease Pressure

```{r}
median(fhb_sev$sev_check)

library(tidyverse)
fhb_sev_coop1 <- fhb_sev_coop %>%
  mutate(sev_check_class = case_when(
      sev_check < 7 ~ "low",
      sev_check >= 7 ~ "high"))

mv_sev_check <- rma.mv(log_sev, vi,
  mods = ~AI2*sev_check_class,
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_coop1
)

mv_sev_check


anova(mv_sev_check, btt= 8:12)

```

### Baseline 10%

```{r}
library(tidyverse)
library(metafor)

fhb_sev_coop2 <- fhb_sev_coop %>%
  mutate(sev_check_class = case_when(
      sev_check < 10 ~ "low",
      sev_check >= 10 ~ "high"))

mv_sev_check <- rma.mv(log_sev, vi,
  mods = ~AI2*sev_check_class,
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_coop2
)

mv_sev_check


anova(mv_sev_check, btt=8:12)
```


### Sev_check as continuous

```{r}

mv_sev_check_cont <- rma.mv(log_sev, vi,
  mods = ~AI2*as.numeric(sev_check),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_coop
)

mv_sev_check_cont


anova(mv_sev_check_cont, btt=8:12)


```

### yield_class

```{r}
#Moderator yield_class

summary(fhb_sev_coop$yld_check) # Median = 2993; Mean = 2880.45 

fhb_sev_coop <- fhb_sev_coop %>%
  mutate(yld_check_class = case_when(
      yld_check < 3000 ~ "low",
      yld_check >= 3000 ~ "high"))
table(fhb_sev_coop$AI2, fhb_sev_coop$yld_check_class)


mv_yld_check <- rma.mv(log_sev, vi,
  mods = ~AI2*factor(yld_check_class),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_coop
)

mv_yld_check


anova(mv_yld_check, btt=8:12)


```

### State

```{r}


# Number of entries by fungicide and state
table(fhb_sev_coop$AI2, fhb_sev_coop$state)


mv_sev_state <- rma.mv(log_sev, vi,
  mods = ~AI2*factor(state),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_coop
)

mv_sev_state

# anova(fhb_mv_AI_state,btt=8:15)
# 
# anova(fhb_mv_AI_state,btt=8:11)
# 
# anova(fhb_mv_AI_state,btt=11:15)

```


### Year as continuous

```{r}

# Number of entries by fungicide and year
table(fhb_sev$AI2, fhb_sev$year)

mv_sev_year <- rma.mv(log_sev, vi,
  mods = ~AI2*year,
  random = list(~AI2 | factor(trial)),
  struct = "HCS",
  method = "ML",
  data = fhb_sev_coop %>% mutate(year = year-2000))


mv_sev_year

anova(mv_sev_year, btt=8:12)


```

# Publications

```{r}
fhb_sev_publ = fhb_sev %>% 
  filter(publication != "Boletim")

```


```{r}
fhb_sev_publ %>%
  tabyl(AI2, publication)

fhb_sev %>%
  tabyl(AI2, publication)
```

## covariance structure

Now we will fit models with CS, HCS and UN matrix-covariance structure. We will then compare them with `anova` function to choose among the best model.

```{r}

library(metafor)


mv_sev_HCS_publ <- rma.mv(log_sev, vi,
  mods = ~AI2,
  random = list(~AI2 | factor(trial)),
  struct = "HCS",
  method = "ML",
  data = fhb_sev_publ
)

mv_sev_publ <- rma.mv(log_sev, vi,
  mods = ~AI2,
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_publ
)

mv_sev_publ
```


We can see below that the UN structure is a better model.

```{r}

anova(mv_sev_HCS_publ, mv_sev_publ)
AIC(mv_sev_HCS_publ)
```


## Percent control

Let's obtain the percent control from the estimated ratios.

```{r}

efficacy_sev_publ <- data.frame(cbind(
  (1 - exp(mv_sev_publ$b)) * 100,
  (1 - exp(mv_sev_publ$ci.lb)) * 100,
  (1 - exp(mv_sev_publ$ci.ub)) * 100
))



efficacy_sev_publ
```

## Contrasts

We can set linear contrasts between treatments of interest and get the P-value using the `anova` function.


```{r}
anova(mv_sev_publ, L = rbind(
  c(0, 1, -1, 0, 0, 0, 0),
  c(0, 1, 0, -1, 0, 0, 0),
  c(0, 1, 0, 0, -1, 0, 0),
  c(0, 1, 0, 0, 0, -1, 0),
  c(0, 1, 0, 0, 0, 0, -1),
  c(0, 0, 1, -1, 0, 0, 0),
  c(0, 0, 1, 0, -1, 0, 0),
  c(0, 0, 1, 0, 0, -1, 0),
  c(0, 0, 1, 0, 0, 0, -1),
  c(0, 0, 0, 1, -1, 0, 0),
  c(0, 0, 0, 1, 0, -1, 0),
  c(0, 0, 0, 1, 0, 0, -1),
  c(0, 0, 0, 0, 1, -1, 0),
  c(0, 0, 0, 0, 1, 0, -1),
  c(0, 0, 0, 0, 0, 1, -1)
))
```

## Moderators

### Cultivar 

```{r}
# creating two groups of cultivars (MR, S)
table(fhb_sev_publ$cultivar, fhb_sev_publ$reaction)
nrow(table(fhb_sev_publ$cultivar, fhb_sev_publ$reaction))

# Renaming the reactions 
library(plyr)
fhb_sev_publ$reaction <- revalue(fhb_sev_publ$reaction, c("MS" = "S"))
fhb_sev_publ$reaction <- revalue(fhb_sev_publ$reaction, c("MS/MR" = "MR"))
fhb_sev_publ$reaction <- revalue(fhb_sev_publ$reaction, c("MR/R" = "MR"))
fhb_sev_publ$reaction <- revalue(fhb_sev_publ$reaction, c("MS/S" = "S"))
detach("package:plyr", unload = TRUE)

table(fhb_sev_publ$cultivar, fhb_sev_publ$reaction)
table(fhb_sev_publ$reaction)
table(fhb_sev_publ$AI2, fhb_sev_publ$reaction)


```

```{r}
library(metafor)


mv_reaction <- rma.mv(log_sev, vi,
  mods = ~AI2*reaction,
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_publ
)

mv_reaction


anova(mv_reaction, btt=9:10)
```

### Disease Pressure

```{r}
median(fhb_sev_publ$sev_check)

library(tidyverse)
fhb_sev_publ <- fhb_sev_publ %>%
  mutate(sev_check_class = case_when(
      sev_check < 7 ~ "low",
      sev_check >= 7 ~ "high"))

mv_sev_check <- rma.mv(log_sev, vi,
  mods = ~AI2*sev_check_class,
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_publ
)

mv_sev_check


anova(mv_sev_check, btt=9:14)

```

### Baseline 10%

```{r}
library(tidyverse)
library(metafor)

fhb_sev_publ <- fhb_sev_publ %>%
  mutate(sev_check_class = case_when(
      sev_check < 10 ~ "low",
      sev_check >= 10 ~ "high"))

mv_sev_check <- rma.mv(log_sev, vi,
  mods = ~AI2*sev_check_class,
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_publ
)

mv_sev_check


anova(mv_sev_check, btt=9:14)
```


### Sev_check as continuous

```{r}

mv_sev_check_cont <- rma.mv(log_sev, vi,
  mods = ~AI2*as.numeric(sev_check),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_publ
)

mv_sev_check_cont


anova(mv_sev_check_cont, btt=9:14)


```

### yield_class

```{r}
#Moderator yield_class

summary(fhb_sev_publ$yld_check) # Median = 2993; Mean = 2880.45 

fhb_sev_publ <- fhb_sev_publ %>%
  mutate(yld_check_class = case_when(
      yld_check < 3000 ~ "low",
      yld_check >= 3000 ~ "high"))
table(fhb_sev_publ$AI2, fhb_sev_publ$yld_check_class)


mv_yld_check <- rma.mv(log_sev, vi,
  mods = ~AI2*factor(yld_check_class),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_publ
)

mv_yld_check


anova(mv_yld_check, btt=9:14)


```

### State

```{r}


# Number of entries by fungicide and state
table(fhb_sev_publ$AI2, fhb_sev_publ$state)


mv_sev_state <- rma.mv(log_sev, vi,
  mods = ~AI2*factor(state),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_publ
)

mv_sev_state

# anova(fhb_mv_AI_state,btt=8:15)
# 
# anova(fhb_mv_AI_state,btt=8:11)
# 
# anova(fhb_mv_AI_state,btt=11:15)

```

### Publication

```{r}
mv_sev_publication <- rma.mv(log_sev, vi,
  mods = ~AI2*factor(publication),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_publ
)

mv_sev_publication

anova(mv_sev_publication, btt=10:16)
```



# Overall 

## covariance structure

Now we will fit models with CS, HCS and UN matrix-covariance structure. We will then compare them with `anova` function to choose among the best model.

```{r}

library(metafor)


mv_sev_HCS <- rma.mv(log_sev, vi,
  mods = ~AI2,
  random = list(~AI2 | factor(trial)),
  struct = "HCS",
  method = "ML",
  data = fhb_sev
)

mv_sev <- rma.mv(log_sev, vi,
  mods = ~AI2,
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev
)

mv_sev
```


We can see below that the UN structure is a better model.

```{r}

anova(mv_sev_HCS, mv_sev)
AIC(mv_sev_HCS)
```


## Percent control

Let's obtain the percent control from the estimated ratios.

```{r}

efficacy_sev <- data.frame(cbind(
  (1 - exp(mv_sev$b)) * 100,
  (1 - exp(mv_sev$ci.lb)) * 100,
  (1 - exp(mv_sev$ci.ub)) * 100
))



efficacy_sev
```

```{r}

efficacy_res = efficacy_sev %>% 
  set_names("efficacy", "eff_sup", "eff_inf") %>% 
  mutate(fungicide = c("check", "AZOX + TEBU 2X", "PIRA + METC 1X", "PIRA + METC 2X", "TEBU 2X", "TFLX + PROT 2X", "TFLX + TEBU 2X")) %>% 
  filter(fungicide != "check")
efficacy_res

library(readr)
write_csv(efficacy_res, "data/efficacy.csv")
```



## Contrasts

We can set linear contrasts between treatments of interest and get the P-value using the `anova` function.


```{r}
anova(mv_sev, L = rbind(
  c(0, 1, -1, 0, 0, 0, 0),
  c(0, 1, 0, -1, 0, 0, 0),
  c(0, 1, 0, 0, -1, 0, 0),
  c(0, 1, 0, 0, 0, -1, 0),
  c(0, 1, 0, 0, 0, 0, -1),
  c(0, 0, 1, -1, 0, 0, 0),
  c(0, 0, 1, 0, -1, 0, 0),
  c(0, 0, 1, 0, 0, -1, 0),
  c(0, 0, 1, 0, 0, 0, -1),
  c(0, 0, 0, 1, -1, 0, 0),
  c(0, 0, 0, 1, 0, -1, 0),
  c(0, 0, 0, 1, 0, 0, -1),
  c(0, 0, 0, 0, 1, -1, 0),
  c(0, 0, 0, 0, 1, 0, -1),
  c(0, 0, 0, 0, 0, 1, -1)
))
```

## Moderators

### Cultivar 

```{r}
# creating two groups of cultivars (MR, S)
table(fhb_sev$cultivar, fhb_sev$reaction)
nrow(table(fhb_sev$cultivar, fhb_sev$reaction))

# Renaming the reactions 
library(plyr)
fhb_sev$reaction <- revalue(fhb_sev$reaction, c("MS" = "S"))
fhb_sev$reaction <- revalue(fhb_sev$reaction, c("MS/MR" = "MR"))
fhb_sev$reaction <- revalue(fhb_sev$reaction, c("MR/R" = "MR"))
fhb_sev$reaction <- revalue(fhb_sev$reaction, c("MS/S" = "S"))
detach("package:plyr", unload = TRUE)

table(fhb_sev$cultivar, fhb_sev$reaction)
table(fhb_sev$reaction)
table(fhb_sev$AI2, fhb_sev$reaction)


```

```{r}
library(metafor)


mv_reaction <- rma.mv(log_sev, vi,
  mods = ~AI2*reaction,
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev
)

mv_reaction


anova(mv_reaction, btt=9:12)
```

### Year as continuous

```{r}

# Number of entries by fungicide and year
table(fhb_sev$AI2, fhb_sev$year)

mv_sev_year <- rma.mv(log_sev, vi,
  mods = ~AI2*year,
  random = list(~AI2 | factor(trial)),
  struct = "HCS",
  method = "ML",
  data = fhb_sev %>% mutate(year = year-2000))


mv_sev_year

anova(mv_sev_year, btt=9:14)


```


### Disease Pressure

```{r}
median(fhb_sev$sev_check)

library(tidyverse)
fhb_sev <- fhb_sev %>%
  mutate(sev_check_class = case_when(
      sev_check < 7 ~ "low",
      sev_check >= 7 ~ "high"))

mv_sev_check <- rma.mv(log_sev, vi,
  mods = ~AI2*sev_check_class,
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev
)

mv_sev_check


anova(mv_sev_check, btt=9:14)

```

### Baseline 10%

```{r}
library(tidyverse)
library(metafor)

fhb_sev <- fhb_sev %>%
  mutate(sev_check_class = case_when(
      sev_check < 10 ~ "low",
      sev_check >= 10 ~ "high"))

mv_sev_check <- rma.mv(log_sev, vi,
  mods = ~AI2*sev_check_class,
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev
)

mv_sev_check


anova(mv_sev_check, btt=9:14)
```


### Sev_check as continuous

```{r}

mv_sev_check_cont <- rma.mv(log_sev, vi,
  mods = ~AI2*as.numeric(sev_check),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev
)

mv_sev_check_cont


anova(mv_sev_check_cont, btt=9:14)


```

### yield_class

```{r}
#Moderator yield_class

summary(fhb_sev$yld_check) # Median = 2993; Mean = 2880.45 

fhb_sev <- fhb_sev %>%
  mutate(yld_check_class = case_when(
      yld_check < 3000 ~ "low",
      yld_check >= 3000 ~ "high"))
table(fhb_sev$AI2, fhb_sev$yld_check_class)


mv_yld_check <- rma.mv(log_sev, vi,
  mods = ~AI2*factor(yld_check_class),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev
)

mv_yld_check


anova(mv_yld_check, btt=9:14)


```


### State

```{r}


# Number of entries by fungicide and state
table(fhb_sev_coop$AI2, fhb_sev_coop$state)


mv_sev_state <- rma.mv(log_sev, vi,
  mods = ~AI2*factor(state),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev
)

mv_sev_state

# anova(fhb_mv_AI_state,btt=8:15)
# 
# anova(fhb_mv_AI_state,btt=8:11)
# 
# anova(fhb_mv_AI_state,btt=11:15)

```

### Publication

```{r}

# Renaming the treatments 
library(plyr)
fhb_sev$publication <- revalue(fhb_sev$publication, c("Boletim" = "AABoletim"))
detach("package:plyr", unload = TRUE)


mv_sev_publication <- rma.mv(log_sev, vi,
  mods = ~AI2*factor(publication),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev
)

mv_sev_publication

anova(mv_sev_publication, btt=11:21)
```

#### Mod effect

```{r}
reg1 = data.frame(mv_sev_publication$beta, mv_sev_publication$ci.lb, mv_sev_publication$ci.ub) %>%
  rownames_to_column("trat") %>%
  separate(trat, into = c("lado1", "lado2"), sep = ":") %>%
  separate(lado2, into = c("lixo","lado3"),sep = "[[)]]" ) %>% 
  select(-lixo) %>%
  separate(lado1, into = c("lixo","lado1"),sep = "AI2" ) %>%
  select(-lixo) %>%
  filter(lado1 == "PIRA + METC 2X") %>% 
  set_names("fungicide", "publication", "estimate", "ci.lb", "ci.ub") %>% 
  mutate(publication = c("Coop.Trials", "Papers", "Abstracts", "Thesis"))

reg2 = reg1%>% 
  group_by(fungicide, publication) %>% 
  summarise(efficacy = (1-exp(first(estimate)+estimate))*100,
            ciu = (1-exp(first(ci.ub)+ ci.ub))*100,
            ci.lb = (1-exp(first(ci.lb)+ci.lb))*100) %>% 
  filter(publication != "Coop.Trials")

reg3 = reg1 %>% 
  filter(publication == "Coop.Trials") %>% 
  group_by(fungicide, publication) %>%
  summarise(efficacy = (1-exp(estimate))*100,
            ciu = (1-exp(ci.ub))*100,
            ci.lb = (1-exp(ci.lb))*100)

reg4 = rbind(reg3,reg2)
reg4
```

# Network Graph



```{r message=FALSE, warning=FALSE}
library(janitor)
library(tidyverse)

fhb_sev <- read_csv("data/dat-sev.csv")

# Renaming the treatments
library(plyr)
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("check-0" = "AACHECK"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Azoxistrobina + Tebuconazole-2" = "AZOX + TEBU 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Piraclostrobina + Metconazole-2" = "PIRA + METC 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Tebuconazole-2" = "TEBU 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Trifloxistrobina + Protioconazole-2" = "TFLX + PROT 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Trifloxistrobina + Tebuconazole-2" = "TFLX + TEBU 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Piraclostrobina + Metconazole-1" = "PIRA + METC 1X"))
detach("package:plyr", unload = TRUE)


fhb_sev %>%
tabyl(AI2)

# Renaming the treatments for the network graph
library(plyr)
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("AACHECK" = "CHECK (61)"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("AZOX + TEBU 2X" = "AZOX + TEBU 2X (25)"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("PIRA + METC 2X" = "PIRA + METC 2X (57)"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("TEBU 2X" = "TEBU 2X (14)"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("TFLX + PROT 2X" = "TFLX + PROT 2X (39)"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("TFLX + TEBU 2X" = "TFLX + TEBU 2X (36)"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("PIRA + METC 1X" = "PIRA + METC 1X (16)"))
detach("package:plyr", unload = TRUE)


```


Now We need to prepare the data to get the network graph. Thus, we used the package `netmeta` with the function `pairwise` to calculate the contrasts.


```{r message=FALSE, warning=FALSE}
library(netmeta)
pair_sev <- pairwise(
  treat = factor(AI2),
  n = 4,
  mean = sev,
  sd = V_sev,
  studlab = trial,
  data = fhb_sev,
  sm = "ROM"
)
```

```{r}
net_sev <- netmeta(TE, seTE, treat1, treat2, studlab, data = pair_sev, sm = "ROM", backtransf = TRUE)
summary(net_sev)
```


A network graph is composed of nodes (fungicide treatments) and edges or links between two treatments directly compared in a same trial. This graph allows to visualize how the treatments relate to each other and the number of direct comparisons can be depicted by the thickness of the edges, but also with numbers presented at the top of the links. 

```{r}

#pdf("Figures/net_sev.pdf", width=10, height=6)
netgraph(net_sev,
  plastic = FALSE,
  col = "gray",
  thickness = "number.of.studies",
  points = TRUE,
  col.points = "black",
  cex.points = c("AZOX + TEBU 2 (25)" = 2.5, "CHECK (61)" = 6, "PIRA + METC 1X (16)" = 1.6, "PIRA + METC 2X (57)" = 5.6, "TEBU 2X (14)" = 1.4, "TFLX + PROT 2X (39)" = 3.8,  "TFLX + TEBU 2X (36)" = 3.5),
  number.of.studies = TRUE,
  cex.number.of.studies = 1.25,
  col.number.of.studies = "black",
  bg.number.of.studies = "white",
  multiarm = FALSE,
  col.multiarm = "gray",
  pos.number.of.studies = 0.50)
#dev.off()
```

## Designs 

```{r}
sev_design <- decomp.design(net_sev)
sev_design$Q.inc.detach
```





