
```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

# Import Data

```{r, warning=FALSE}
library(readr)
library(tidyverse)
library(janitor)
fhb_yld1 <- read_csv("data/dat-yld.csv")

target <- c("check-0", "Azoxistrobina + Tebuconazole-2", "Piraclostrobina + Metconazole-2", "Tebuconazole-2", "Trifloxistrobina + Protioconazole-2", "Trifloxistrobina + Tebuconazole-2", "Piraclostrobina + Metconazole-1") 
fhb_yld <- fhb_yld1 %>%
  group_by(trial) %>% 
  filter(AI2 %in% target) %>% 
  mutate(n2 = n()) %>% 
  filter(n2 != 1)

# Renaming the treatments 
library(plyr)
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("check-0" = "AACHECK"))
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("Azoxistrobina + Tebuconazole-2" = "AZOX + TEBU 2X"))
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("Piraclostrobina + Metconazole-2" = "PYRA + METC 2X"))
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("Tebuconazole-2" = "TEBU 2X"))
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("Trifloxistrobina + Protioconazole-2" = "TFLX + PROT 2X"))
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("Trifloxistrobina + Tebuconazole-2" = "TFLX + TEBU 2X"))
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("Piraclostrobina + Metconazole-1" = "PYRA + METC 1X"))
detach("package:plyr", unload = TRUE)

```


## Sampling Variance

```{r}
# Sampling variance for log of the mean (Paul et al., 2008) to use in multivariate model
fhb_yld <- fhb_yld%>%
  mutate(log_yld = log(yld))

fhb_yld$log_var_yld <- with(fhb_yld, V_yld / (n * yld^2))

# Calculate the variation of absolute yield

fhb_yld$var_yld <- fhb_yld$V_yld/fhb_yld$n # multivariate approach


```

## Absolute yield (kg/ha)

```{r}

library(metafor)

mv_yld <- rma.mv(yld, var_yld,
  mods = ~AI2,
  random = list(~AI2 | trial),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_yld
)

summary(mv_yld)
```


```{r}
yield_res<- data.frame(cbind(mv_yld$b, 
                             mv_yld$ci.lb,
                             mv_yld$ci.ub)) %>% 
  set_names("yld", "yld_inf", "yld_sup") %>% 
  mutate(fungicide = c("check", "AZOX + TEBU 2X", "PYRA + METC 1X", "PYRA + METC 2X", "TEBU 2X", "TFLX + PROT 2X", "TFLX + TEBU 2X")) %>% 
  filter(fungicide != "check")
yield_res

library(readr)
write_csv(yield_res, "data/yld_absolute.csv")

library(tidyverse)
efficacy_res <- read_csv("data/efficacy.csv")


sev_yld = full_join(efficacy_res, yield_res)
sev_yld

library(readr)
write_csv(sev_yld, "data/sev_yld.csv")
```


### Contrasts

We can set linear contrasts between treatments of interest and get the P-valued using the `anova` function.

```{r}
anova(mv_yld, L = rbind(
  c(0, 1, -1, 0, 0, 0, 0),
  c(0, 1, 0, -1, 0, 0, 0),
  c(0, 1, 0, 0, -1, 0, 0),
  c(0, 1, 0, 0, 0, -1, 0),
  c(0, 1, 0, 0, 0, 0, -1),
  c(0, 0, 1, -1, 0, 0, 0),
  c(0, 0, 1, 0, -1, 0, 0),
  c(0, 0, 1, 0, 0, -1, 0),
  c(0, 0, 1, 0, 0, 0, -1),
  c(0, 0, 0, 1, -1, 0, 0),
  c(0, 0, 0, 1, 0, -1, 0),
  c(0, 0, 0, 1, 0, 0, -1),
  c(0, 0, 0, 0, 1, -1, 0),
  c(0, 0, 0, 0, 1, 0, -1),
  c(0, 0, 0, 0, 0, 1, -1)
))
```


## Relative yield (%)

```{r}
mv_yld_relative <- rma.mv(log_yld, log_var_yld,
  mods = ~AI2,
  random = list(~AI2 | trial),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_yld
)

summary(mv_yld_relative)
```

## Percent yield

```{r}
results_relative_yld<- data.frame(cbind((exp(mv_yld_relative$b)-1)*100, 
                             (exp(mv_yld_relative$ci.lb)-1)*100,
                             (exp(mv_yld_relative$ci.ub)-1)*100)) %>%  
  set_names("yld_rel", "yld_rel_inf", "yld_rel_sup") %>% 
  mutate(fungicide = c("check", "AZOX + TEBU 2X", "PYRA + METC 1X", "PYRA + METC 2X", "TEBU 2X", "TFLX + PROT 2X", "TFLX + TEBU 2X")) %>% 
  filter(fungicide != "check")
results_relative_yld

library(readr)
write_csv(results_relative_yld, "data/yld_relative.csv")
```


## Moderator analysis

The model was expanded to include categorical or continuous moderator variables that could explain, at least portion of, the heterogeneity of the effects across trials.

### Year as continuous

We tested Year as continuous to check whether there was any trend of decline in wheat grain yield over time.

```{r}

# Number of entries by fungicide and year
table(fhb_yld$AI2, fhb_yld$year)

mv_yld_year <- rma.mv(yld, var_yld,
  mods = ~AI2*as.numeric(year),
  random = list(~AI2 | factor(trial)),
  struct = "HCS",
  method = "ML",
  data = fhb_yld %>% mutate(year = year-2000))

mv_yld_year

anova(mv_yld_year, btt=9:14)
```

### Disease Pressure

We created this baseline for FHB disease index based on the median of the mean values in the nontreated check.

```{r}


library(tidyverse)
fhb_yld <- fhb_yld %>%
  mutate(sev_check_class = case_when(
      sev_check < 7 ~ "low",
      sev_check >= 7 ~ "high"))

mv_dis_press <- rma.mv(yld, var_yld,
  mods = ~AI2*factor(sev_check_class),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_yld
)

mv_dis_press


anova(mv_dis_press, btt=9:14)
```


### Sev_check as continuous

```{r}

mv_sev_check_cont <- rma.mv(yld, var_yld,
  mods = ~AI2*as.numeric(sev_check),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_yld
)

mv_sev_check_cont


anova(mv_sev_check_cont, btt=9:14)


```

### yield_class

We created this baseline for wheat grain yield based on the median of the mean values in the nontreated check.

```{r}
#Moderator yield_class

summary(fhb_yld$yld_check)

fhb_yld <- fhb_yld %>%
  mutate(yld_check_class = case_when(
      yld_check < 3000 ~ "low",
      yld_check >= 3000 ~ "high"))
table(fhb_yld$AI2, fhb_yld$yld_check_class)


mv_yld_check <- rma.mv(yld, var_yld,
  mods = ~AI2*factor(yld_check_class),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_yld
)

mv_yld_check


anova(mv_yld_check, btt=9:14)


```


## Inconsistency

In a network meta-analysis, it is important to check whether the results are consistent across the different designs. We included this variable and tested the interaction effect of treatments and design group.

```{r}
library(readr)
library(tidyverse)
library(janitor)
fhb_yld1 <- read_csv("data/dat-yld.csv")

target <- c("check-0", "Azoxistrobina + Tebuconazole-2", "Piraclostrobina + Metconazole-2", "Tebuconazole-2", "Trifloxistrobina + Protioconazole-2", "Trifloxistrobina + Tebuconazole-2", "Piraclostrobina + Metconazole-1") 
fhb_yld <- fhb_yld1 %>%
  group_by(trial) %>% 
  filter(AI2 %in% target) %>% 
  mutate(n2 = n()) %>% 
  filter(n2 != 1)

# Renaming the treatments 
library(plyr)
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("check-0" = "AACHECK"))
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("Azoxistrobina + Tebuconazole-2" = "AZOX + TEBU 2X"))
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("Piraclostrobina + Metconazole-2" = "PYRA + METC 2X"))
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("Tebuconazole-2" = "TEBU 2X"))
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("Trifloxistrobina + Protioconazole-2" = "TFLX + PROT 2X"))
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("Trifloxistrobina + Tebuconazole-2" = "TFLX + TEBU 2X"))
fhb_yld$AI2 <- revalue(fhb_yld$AI2, c("Piraclostrobina + Metconazole-1" = "PYRA + METC 1X"))
detach("package:plyr", unload = TRUE)

fhb_yld$var_yld <- fhb_yld$V_yld/fhb_yld$n # multivariate approach
```


### Design groups

Eleven different designs (here design refers to the set of treatments in the trial) were found in the trials reporting yield.

```{r}
library(tidyverse)
design1 = fhb_yld %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "TFLX + PROT 2X", "TFLX + TEBU 2X", "AZOX + TEBU 2X", "TEBU 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(1, length(AI2))) %>% 
  select(1:5,8:15,17:23) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design1

design2 = fhb_yld %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "TFLX + PROT 2X", "TFLX + TEBU 2X", "AZOX + TEBU 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(2, length(AI2))) %>% 
  select(1:5,8:15,17:23) %>%    
  filter(n2 == 5) %>% 
  filter(n3 == 5)
design2

design3 = fhb_yld %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "TEBU 2X","PYRA + METC 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(3, length(AI2))) %>% 
  select(1:5,8:15,17:23) %>%   
  filter(n2 == 3) %>% 
  filter(n3 == 3)
design3

design4 = fhb_yld %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "TFLX + PROT 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(4, length(AI2))) %>% 
  select(1:5,8:15,17:23) %>%  
  filter(n2 == 3) %>% 
  filter(n3 == 3)
design4

design5 = fhb_yld %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "TFLX + PROT 2X", "TFLX + TEBU 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(5, length(AI2))) %>% 
  select(1:5,8:15,17:23) %>%   
  filter(n2 == 4) %>% 
  filter(n3 == 4)
design5

design6 = fhb_yld %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "PYRA + METC 1X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(6, length(AI2))) %>% 
  select(1:5,8:15,17:23) %>%    
  filter(n2 == 3) %>% 
  filter(n3 == 3)
design6

design7 = fhb_yld %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "TEBU 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(7, length(AI2))) %>% 
  select(1:5,8:15,17:23) %>%    
  filter(n2 == 2) %>% 
  filter(n3 == 2)
design7

design8 = fhb_yld %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(8, length(AI2))) %>% 
  select(1:5,8:15,17:23) %>%    
  filter(n2 == 2) %>% 
  filter(n3 == 2)
design8

design9 = fhb_yld %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "TFLX + PROT 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(9, length(AI2))) %>% 
  select(1:5,8:15,17:23) %>%    
  filter(n2 == 2) %>% 
  filter(n3 == 2)
design9

design10 = fhb_yld %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "PYRA + METC 1X",  "TEBU 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(10, length(AI2))) %>% 
  select(1:5,8:15,17:23) %>%  
  filter(n2 == 4) %>% 
  filter(n3 == 4)
design10

design11 = fhb_yld %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "PYRA + METC 1X", "TFLX + PROT 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(11, length(AI2))) %>% 
  select(1:5,8:15,17:23) %>%    
  filter(n2 == 4) %>% 
  filter(n3 == 4)
design11

fhb_yld_design = rbind(design1, design2, design3, design4, design5, design6, design7, design8, design9, design10, design11) %>% 
  group_by(trial)
fhb_yld_design

```

### Test 

We used a factorial-type ANOVA model to determine the significance of the *treatment x design* interaction, evaluated based on the Wald test statistic.


```{r}
library(metafor)
mv_incon <- rma.mv(yld, var_yld,
  mods = ~AI2 * design,
  random = list(~ design / AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_yld_design)
mv_incon
anova(mv_incon, btt = 9:14)

```

