

```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

# Import Data

```{r}
library(knitr)
library(tidyverse)
library(janitor)
fhb_sev <- read_csv("data/dat-sev.csv")

fhb_sev %>%
  tabyl(AI2, n_spray)

# Renaming the treatments 
library(plyr)
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("check-0" = "AACHECK"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Azoxistrobina + Tebuconazole-2" = "AZOX + TEBU 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Piraclostrobina + Metconazole-2" = "PYRA + METC 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Tebuconazole-2" = "TEBU 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Trifloxistrobina + Protioconazole-2" = "TFLX + PROT 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Trifloxistrobina + Tebuconazole-2" = "TFLX + TEBU 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Piraclostrobina + Metconazole-1" = "PYRA + METC 1X"))
detach("package:plyr", unload = TRUE)


# create the log of the FHB index variable
fhb_sev <- fhb_sev %>%
  mutate(log_sev = log(sev))

# create the sampling variance for the log of FHB index
fhb_sev$vi <- with(fhb_sev, V_sev / (n * sev^2))


```


## Covariance structure

Now we will fit models with HCS and UN matrix-covariance structure. We will then compare them with `anova` function to choose among the best model.

```{r}
summary(fhb_sev$vi)
library(metafor)
fhb_sev = fhb_sev %>% #only study 100 has vi>25. So, we excluded that study in order to obtain stable results
  filter(vi < 25)


mv_sev_HCS <- rma.mv(log_sev, vi,
  mods = ~AI2,
  random = list(~AI2 | factor(trial)),
  struct = "HCS",
  method = "ML",
  data = fhb_sev
)

mv_sev <- rma.mv(log_sev, vi,
  mods = ~AI2,
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev
)

mv_sev
```


We can see below that the UN structure is a better model.

```{r}

anova(mv_sev_HCS, mv_sev)
AIC(mv_sev_HCS)
```


## Percent control

Let's obtain the percent control from the estimated ratios.

```{r}

efficacy_sev <- data.frame(cbind(
  (1 - exp(mv_sev$b)) * 100,
  (1 - exp(mv_sev$ci.lb)) * 100,
  (1 - exp(mv_sev$ci.ub)) * 100))

efficacy_sev

# Let's save the results
efficacy_res = efficacy_sev %>% 
  set_names("efficacy", "eff_sup", "eff_inf") %>% 
  mutate(fungicide = c("check", "AZOX + TEBU 2X", "PYRA + METC 1X", "PYRA + METC 2X", "TEBU 2X", "TFLX + PROT 2X", "TFLX + TEBU 2X")) %>% 
  filter(fungicide != "check")
efficacy_res

library(readr)
write_csv(efficacy_res, "data/efficacy.csv")
```


## Contrasts

We can set linear contrasts between treatments of interest and get the P-value using the `anova` function.


```{r}
anova(mv_sev, L = rbind(
  c(0, 1, -1, 0, 0, 0, 0),
  c(0, 1, 0, -1, 0, 0, 0),
  c(0, 1, 0, 0, -1, 0, 0),
  c(0, 1, 0, 0, 0, -1, 0),
  c(0, 1, 0, 0, 0, 0, -1),
  c(0, 0, 1, -1, 0, 0, 0),
  c(0, 0, 1, 0, -1, 0, 0),
  c(0, 0, 1, 0, 0, -1, 0),
  c(0, 0, 1, 0, 0, 0, -1),
  c(0, 0, 0, 1, -1, 0, 0),
  c(0, 0, 0, 1, 0, -1, 0),
  c(0, 0, 0, 1, 0, 0, -1),
  c(0, 0, 0, 0, 1, -1, 0),
  c(0, 0, 0, 0, 1, 0, -1),
  c(0, 0, 0, 0, 0, 1, -1)
))
```

## Moderators

The model was expanded to include categorical or continuous moderator variables that could explain, at least portion of, the heterogeneity of the effects across trials.

### Year as continuous

We tested Year as continuous to check whether there was any trend of decline in fungicide efficacy over time.

```{r}

# Number of entries by fungicide and year
table(fhb_sev$AI2, fhb_sev$year)

mv_sev_year <- rma.mv(log_sev, vi,
  mods = ~AI2*year,
  random = list(~AI2 | factor(trial)),
  struct = "HCS",
  method = "ML",
  data = fhb_sev %>% mutate(year = year-2000))


mv_sev_year

anova(mv_sev_year, btt=9:14)


```


### Disease Pressure

We created this baseline for FHB disease index based on the median of the mean values in the nontreated check.

```{r}
median(fhb_sev$sev_check)

library(tidyverse)
fhb_sev <- fhb_sev %>%
  mutate(sev_check_class = case_when(
      sev_check < 7 ~ "low",
      sev_check >= 7 ~ "high"))

mv_sev_check <- rma.mv(log_sev, vi,
  mods = ~AI2* factor(sev_check_class),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev
)

mv_sev_check


anova(mv_sev_check, btt=9:14)

```

### Baseline 10%

We also tested if the baseline of 10%, which is used in the United States to define an FHB epidemic case (De Wolf et al. 2003), could explain, at least portion of, the heterogeneity of the effects across trials.

```{r}
library(tidyverse)
library(metafor)

fhb_sev <- fhb_sev %>%
  mutate(sev_check_class = case_when(
      sev_check < 10 ~ "low",
      sev_check >= 10 ~ "high"))

mv_sev_check <- rma.mv(log_sev, vi,
  mods = ~AI2*factor(sev_check_class),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev
)

mv_sev_check


anova(mv_sev_check, btt=9:14)
```


### Sev_check as continuous

```{r}

mv_sev_check_cont <- rma.mv(log_sev, vi,
  mods = ~AI2*as.numeric(sev_check),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev
)

mv_sev_check_cont


anova(mv_sev_check_cont, btt=9:14)


```

### yield_class

We created this baseline for wheat grain yield based on the median of the mean values in the nontreated check.

```{r}

summary(fhb_sev$yld_check)  

fhb_sev <- fhb_sev %>%
  mutate(yld_check_class = case_when(
      yld_check < 3000 ~ "low",
      yld_check >= 3000 ~ "high"))
table(fhb_sev$AI2, fhb_sev$yld_check_class)


mv_yld_check <- rma.mv(log_sev, vi,
  mods = ~AI2*factor(yld_check_class),
  random = list(~AI2 | factor(trial)),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev
)

mv_yld_check


anova(mv_yld_check, btt=9:14)


```


## Inconsistency


In a network meta-analysis, it is important to check whether the results are consistent across the different designs. We included this variable and tested the interaction effect of treatments and design group.

```{r, warning=FALSE}
library(knitr)
library(tidyverse)
library(janitor)
fhb_sev <- read_csv("data/dat-sev.csv")

fhb_sev %>%
  tabyl(AI2, n_spray)

# Renaming the treatments 
library(plyr)
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("check-0" = "AACHECK"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Azoxistrobina + Tebuconazole-2" = "AZOX + TEBU 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Piraclostrobina + Metconazole-2" = "PYRA + METC 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Tebuconazole-2" = "TEBU 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Trifloxistrobina + Protioconazole-2" = "TFLX + PROT 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Trifloxistrobina + Tebuconazole-2" = "TFLX + TEBU 2X"))
fhb_sev$AI2 <- revalue(fhb_sev$AI2, c("Piraclostrobina + Metconazole-1" = "PYRA + METC 1X"))
detach("package:plyr", unload = TRUE)


# create the log of the FHB index variable
fhb_sev <- fhb_sev %>%
  mutate(log_sev = log(sev))

# create the sampling variance for the log of FHB index
fhb_sev$vi <- with(fhb_sev, V_sev / (n * sev^2))
```

### Design groups

Eleven different designs (here design refers to the set of treatments in the trial) were found in the trials reporting FHB index.

```{r}
design1 = fhb_sev %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "TFLX + PROT 2X", "TFLX + TEBU 2X", "AZOX + TEBU 2X", "TEBU 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(1, length(AI2))) %>% 
  select(1:5,8:15,17:24) %>% 
  filter(n2 == 6) %>% 
  filter(n3 == 6)
design1

design2 = fhb_sev %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "TFLX + PROT 2X", "TFLX + TEBU 2X", "AZOX + TEBU 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(2, length(AI2))) %>% 
  select(1:5,8:15,17:24) %>%   
  filter(n2 == 5) %>% 
  filter(n3 == 5)
design2

design3 = fhb_sev %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "TFLX + TEBU 2X", "AZOX + TEBU 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(3, length(AI2))) %>% 
  select(1:5,8:15,17:24) %>%  
  filter(n2 == 3) %>% 
  filter(n3 == 3)
design3

design4 = fhb_sev %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "PYRA + METC 1X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(4, length(AI2))) %>% 
  select(1:5,8:15,17:24) %>% 
  filter(n2 == 3) %>% 
  filter(n3 == 3)
design4

design5 = fhb_sev %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "TFLX + PROT 2X", "TFLX + TEBU 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(5, length(AI2))) %>% 
  select(1:5,8:15,17:24) %>% 
  filter(n2 == 4) %>% 
  filter(n3 == 4)
design5

design6 = fhb_sev %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "TFLX + PROT 2X", "TFLX + TEBU 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(6, length(AI2))) %>% 
  select(1:5,8:15,17:24) %>%  
  filter(n2 == 3) %>% 
  filter(n3 == 3)
design6

design7 = fhb_sev %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "TEBU 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(7, length(AI2))) %>% 
  select(1:5,8:15,17:24) %>%  
  filter(n2 == 2) %>% 
  filter(n3 == 2)
design7

design8 = fhb_sev %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "TFLX + PROT 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(8, length(AI2))) %>% 
  select(1:5,8:15,17:24) %>%  
  filter(n2 == 3) %>% 
  filter(n3 == 3)
design8

design9 = fhb_sev %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(9, length(AI2))) %>% 
  select(1:5,8:15,17:24) %>%  
  filter(n2 == 2) %>% 
  filter(n3 == 2)
design9

design10 = fhb_sev %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "PYRA + METC 1X", "TFLX + PROT 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(10, length(AI2))) %>% 
  select(1:5,8:15,17:24) %>%  
  filter(n2 == 4) %>% 
  filter(n3 == 4)
design10

design11 = fhb_sev %>% 
  group_by(trial) %>% 
  filter(AI2  %in% c("AACHECK", "PYRA + METC 2X", "TEBU 2X")) %>% 
  mutate(n3 = n()) %>% 
  mutate(design = rep(11, length(AI2))) %>% 
  select(1:5,8:15,17:24) %>%  
  filter(n2 == 3) %>% 
  filter(n3 == 3)
design11

fhb_sev_design = rbind(design1, design2, design3, design4, design5, design6, design7, design8, design9, design10, design11) %>% 
  group_by(trial)
fhb_sev_design
```

### Test 

We used a factorial-type ANOVA model to determine the significance of the *treatment x design* interaction, evaluated based on the Wald test statistic.

```{r}
library(metafor)
summary(fhb_sev_design$vi)

fhb_sev_design = fhb_sev_design %>% 
  filter(vi < 25)

mv_incon <- rma.mv(log_sev, vi,
  mods = ~AI2 * design,
  random = list(~factor(trial) | design / AI2),
  struct = "UN",
  method = "ML",
  control = list(optimizer = "nlm"),
  data = fhb_sev_design)
mv_incon
anova(mv_incon, btt = 9:14)

```
