
```{r}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```


# Import Data

```{r setup, include=FALSE}

library(tidyverse)
library(metafor)
library(ggthemes)
library(cowplot)
library(scales)
library(knitr)
library(broom)
library(dplyr)
library(readxl)
library(gsheet)
library(patchwork)


fhb_base<- gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/1Kh0474vS9xCxwud6RSZgr7VeWEF7FAnYDSi3EMb_bYs/edit#gid=0", sheetid = "data-prod")

target <- c("check-0", "Azoxistrobina + Tebuconazole-2", "Piraclostrobina + Metconazole-2", "Piraclostrobina + Metconazole-1", "Trifloxistrobina + Protioconazole-2", "Trifloxistrobina + Tebuconazole-2", "Tebuconazole-2")

fhb2 <- fhb_base %>%
  mutate(AI2 = paste(AI, n_spray, sep = "-")) %>% 
  filter(AI2 %in% target) %>% 
  filter(year != "NA") %>% 
  filter(AI2 != "NA") %>% 
  filter(sev != "NA") %>% 
  filter(sev > 0) %>% 
  filter(yld != "NA") %>% 
  filter(yld > 0) 


# Renaming the treatments 
library(plyr)
fhb2$AI2 <- revalue(fhb2$AI2, c("check-0" = "CHECK"))
fhb2$AI2 <- revalue(fhb2$AI2, c("Azoxistrobina + Tebuconazole-2" = "AZOX + TEBU"))
fhb2$AI2 <- revalue(fhb2$AI2, c("Piraclostrobina + Metconazole-2" = "PYRA + METC"))
fhb2$AI2 <- revalue(fhb2$AI2, c("Tebuconazole-2" = "TEBU"))
fhb2$AI2 <- revalue(fhb2$AI2, c("Trifloxistrobina + Protioconazole-2" = "TFLX + PROT"))
fhb2$AI2 <- revalue(fhb2$AI2, c("Trifloxistrobina + Tebuconazole-2" = "TFLX + TEBU"))
fhb2$AI2 <- revalue(fhb2$AI2, c("Piraclostrobina + Metconazole-1" = "PYRA + METC 1X"))
detach("package:plyr", unload = TRUE)


fhb2 <- fhb2 %>%
  mutate(state1 = case_when(
      state == "PR" ~ "PR",
      state == "RS" ~ "RS+SC",
      state == "SC" ~ "RS+SC"))

```


## Histogramas

Histograms to check data distribution of FHB index and wheat grain yield. Log-transformed FHB index data was use in the meta-analysis. 

```{r fig.height=8, fig.width=5, warning=FALSE}
## Log of the Effect-sizes
fhb2 <- fhb2 %>%
  mutate(
    log_sev = log(sev),
    log_yld = log(yld))


hist_log_sev <- ggplot(fhb2, aes(log_sev)) + 
  geom_histogram(bins=20, fill = "steelblue", color = "white") + 
  theme_minimal_hgrid() + 
  xlab("log(FHB Index)")


hist_sev <- ggplot(fhb2, aes(sev)) + 
  geom_histogram(bins=20, fill = "steelblue", color = "white") + 
  theme_minimal_hgrid() + 
  xlab("FHB Index (%)")



hist_yld <- ggplot(fhb2, aes(yld)) + 
  geom_histogram(bins=20, fill = "steelblue", color = "white") + 
  theme_minimal_hgrid() +
  xlab("Yield (Kg/ha)")


library(cowplot)
hist_plot <- plot_grid(hist_sev, hist_log_sev, hist_yld, labels = c("A", "B", "C"), nrow = 3, align = "V")
hist_plot


ggsave("Figures/histograms.png", width = 5, height = 8, dpi = 300)
```


## Boxplots

### Severity

```{r message=FALSE, warning=FALSE}

fhb2 <- fhb2  
fhb2$AI2 <- factor(fhb2$AI2, levels = c("CHECK", "AZOX + TEBU", "TFLX + TEBU", "TEBU", "TFLX + PROT", "PYRA + METC", "PYRA + METC 1X"))

box_sev <- ggplot(fhb2, aes(AI2, sev)) +
  geom_boxplot(size = 0.6, outlier.shape = NA) +
  geom_jitter(width = 0.15, size = 2, color = "#83CAFF", alpha = 0.5) +
  theme_minimal_hgrid()+
  labs(x = "Fungicides", y = "FHB Index (%)") +
  scale_y_continuous(breaks = c(0,20,40,60,80,100), limits = c(0,100))+
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size=12),
        axis.title.y = element_text(size=14, face = "bold"))
box_sev

sev_year <- fhb2 %>%
  filter(AI2 == "CHECK") %>%
  ggplot(aes(factor(year), sev_check)) +
  geom_boxplot(size = 0.6, outlier.shape = NA) +
  geom_jitter(width = 0.15, size = 2, color = "#83CAFF", alpha = 0.5) +
  theme_minimal_hgrid()+
  labs(x = "Crop Seasons", y = "FHB Index (%) in the CHECK") +
  scale_y_continuous(breaks = c(0,20,40,60,80,100), limits = c(0,100))+
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size=12),
        axis.title.y = element_text(size=14, face = "bold"))
sev_year

```


### Yield

```{r, message=FALSE, warning=FALSE}
fhb2 <- fhb2  
fhb2$AI2 <- factor(fhb2$AI2, levels = c("CHECK", "AZOX + TEBU", "TFLX + TEBU", "TEBU", "TFLX + PROT", "PYRA + METC", "PYRA + METC 1X"))

box_yld <- ggplot(fhb2, aes(AI2, yld)) +
  geom_boxplot(size = 0.6, outlier.shape = NA) +
  geom_jitter(width = 0.15, size = 2, color = "#FF950E", alpha = 0.5) +
  theme_minimal_hgrid()+
  labs(x = "Fungicides", y = "Yield (kg/ha)") +
  scale_y_continuous(breaks = c(0,1000,2000,3000,4000,5000,6000), limits = c(0, 6000))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=12),
        axis.text.y = element_text(size=12),
        axis.title = element_text(size=14, face = "bold"))
box_yld

yld_year <- fhb2 %>%
  filter(AI2 == "CHECK") %>%
  ggplot(aes(factor(year), yld_check)) +
  geom_boxplot(size = 0.6, outlier.shape = NA) +
  geom_jitter(width = 0.15, size = 2, color = "#FF950E", alpha = 0.5) +
  theme_minimal_hgrid()+
  labs(x = "Crop Seasons", y = "Yield (kg/ha) in the CHECK") +
  scale_y_continuous(breaks = c(0,1000,2000,3000,4000,5000,6000), limits = c(0, 6000))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size=12),
        axis.text.y = element_text(size=12),
         axis.title = element_text(size=14, face = "bold"))
yld_year

```


```{r fig.height=10, fig.width=12}
library(patchwork)

((sev_year + labs(tag = 'A')) / yld_year) | ((box_sev + labs(tag = 'B')) / box_yld)

ggsave("Figures/Combo.png", width = 12, height = 10, dpi = 300)
```


## State

```{r fig.height=8, fig.width=10}

state_sev <- fhb2 %>%
  filter(AI2 == "CHECK") %>%
  ggplot(aes(factor(year), sev_check)) +
  geom_boxplot(size = 0.6, outlier.shape = NA) +
  geom_jitter(width = 0.15, size = 2, color = "#83CAFF", alpha = 0.5) +
  theme_minimal_hgrid()+
  scale_y_continuous(breaks = c(0,25,50,75,100), limits = c(0,100))+
  theme(legend.position = "none",
        strip.text.x = element_text(color = "white",size = 14, face = "bold"),
        strip.background = element_rect(fill = "black"), 
        axis.text = element_text(size = 12),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title = element_text(size=14, face = "bold"))+
  labs(x = "Crop Seasons", y = "FHB Index in the CHECK (%)")+
  facet_wrap(~state1, ncol = 1)
state_sev


state_yld <- fhb2 %>%
  filter(AI2 == "CHECK") %>%
  ggplot(aes(factor(year), yld_check)) +
  geom_boxplot(size = 0.6, outlier.shape = NA) +
  geom_jitter(width = 0.15, size = 2, color = "#FF950E", alpha = 0.5) +
  theme_minimal_hgrid()+
  labs(x = "Crop Seasons", y = "Yield in the CHECK (kg/ha)") +
  scale_y_continuous(breaks = c(0,2000,4000,6000), limits = c(0, 6000))+
  theme(strip.text.x = element_text(color = "white",size = 14, face = "bold"),
        strip.background = element_rect(fill = "black"), 
        axis.text = element_text(size = 12),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title = element_text(size=14, face = "bold"))+
  facet_wrap(~state1, ncol = 1)
state_yld

library(patchwork)

state_sev + labs(tag = 'A') + state_yld + labs(tag = 'B')

ggsave("Figures/Box_state.png", width = 12, height = 8, dpi = 300)

```


## Severity x Yield

Here we ploted the relationship between control efficacy and yield differences.

```{r fig.height=6, fig.width=8}
library(palettetown)
sev_yld <- read_csv("data/sev_yld.csv")
sev_yld

# Renaming the treatments 
library(plyr)
sev_yld$fungicide <- revalue(sev_yld$fungicide, c("AZOX + TEBU 2X" = "AZOX + TEBU"))
sev_yld$fungicide <- revalue(sev_yld$fungicide, c("PYRA + METC 2X" = "PYRA + METC"))
sev_yld$fungicide <- revalue(sev_yld$fungicide, c("TEBU 2X" = "TEBU"))
sev_yld$fungicide <- revalue(sev_yld$fungicide, c("TFLX + PROT 2X" = "TFLX + PROT"))
sev_yld$fungicide <- revalue(sev_yld$fungicide, c("TFLX + TEBU 2X" = "TFLX + TEBU"))
sev_yld$fungicide <- revalue(sev_yld$fungicide, c("PYRA + METC 1X" = "PYRA + METC 1X"))
detach("package:plyr", unload = TRUE)

sev_yld %>% 
  mutate(fungicide = factor(fungicide, levels = c("PYRA + METC", "TFLX + PROT", "TEBU", "AZOX + TEBU", "TFLX + TEBU",  "PYRA + METC 1X"))) %>% 
  ggplot(aes(efficacy, yld)) +
  geom_errorbar(aes(ymin = yld_inf, ymax = yld_sup), width = 0, size = 0.8, color = "black", alpha = 0.35) +
  geom_errorbarh(aes(xmin = eff_inf,xmax = eff_sup),  height = 0, size = 0.8, color = "black", alpha = 0.35)+
  labs(x = "FHB control (%)", y = "Yield difference (kg/ha)", color = "Fungicide")+
  geom_point(aes(efficacy, yld, color = fungicide), size= 3) +
  scale_color_calc()+
  theme_minimal_grid()+
  theme(axis.text=element_text(size=12), 
        axis.title=element_text(size=12, face = "bold"), 
        legend.position = "right",
        legend.title.align = 0.5,
        legend.title = element_text(size=12, face = "bold"))

ggsave("Figures/sev_yld.png", width = 8, height = 5, dpi = 300)
```


## Wheat price

We gathered the wheat price for three wheat-producing states (Rio Grande do Sul, Paraná, and Santa Catarina).

```{r}
library(gsheet)

wheat_price <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1Kh0474vS9xCxwud6RSZgr7VeWEF7FAnYDSi3EMb_bYs/edit#gid=1133011953") 


wheat_price = wheat_price %>% 
  mutate(price_ton = ((price/60)*1000)/5.2)
mean(wheat_price$price_ton)

```


## Tetris plot

Tile plots of the probability classes of breaking even on fungicide costs were produced for each fungicide. 

```{r fig.height=4, fig.width=9}

fhb_tetris <- gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/1Kh0474vS9xCxwud6RSZgr7VeWEF7FAnYDSi3EMb_bYs/edit#gid=1373111570",
  sheetid = "tetris")
fhb_tetris <- fhb_tetris %>%
  mutate(
    tau = as.numeric(tau),
    D = as.numeric(D)
  )


prob <- function(C, P, tau, D) {
  profit <- (D - (C / (P / 1000))) / sqrt(tau) # loss
  prob_gain <- pnorm(profit)
  ploss <- 1 - prob_gain
  ploss
}



for (i in 1:length(fhb_tetris$C)) {
  fhb_tetris$breacking_even[i] <- prob(C = fhb_tetris$C[i], D = fhb_tetris$D[i], tau = fhb_tetris$tau[i], P = fhb_tetris$P[i]) * 100
}


library(viridis)
library(tidyverse)
library(ggthemes)
dat <- fhb_tetris %>%
  mutate(
    breacking_even = as.numeric(breacking_even),
    breacking_even = round(breacking_even, 1)
  )
summary(dat$breacking_even)

library(plyr)
dat$fungicide <- revalue(dat$fungicide, c("AZOX + TEBU 2X" = "AZOX + TEBU"))
dat$fungicide <- revalue(dat$fungicide, c("PYRA + METC 2X" = "PYRA + METC"))
dat$fungicide <- revalue(dat$fungicide, c("TEBU 2X" = "TEBU"))
dat$fungicide <- revalue(dat$fungicide, c("PYRA + METC 1X" = "PYRA + METC 1X"))
detach("package:plyr", unload = TRUE)

dat %>%
  filter(fungicide %in% c("PYRA + METC", "PYRA + METC 1X", "TEBU")) %>% 
  #mutate(fungicide = factor(fungicide, levels = c("PYRA + METC 2X", "AZOX + TEBU 2X","TEBU 2X"))) %>%
  mutate(fungicide = factor(fungicide, levels = c("PYRA + METC", "TEBU", "PYRA + METC 1X"))) %>%
  mutate(breacking_even1 = case_when(
    breacking_even >= 75 ~ "p \u2265 75  ",
    breacking_even < 75 & breacking_even >= 65 ~ "65 \u2264 p < 75  ",
    breacking_even < 65 & breacking_even >= 55 ~ "55 \u2264 p < 65  ",
    breacking_even < 55 & breacking_even >= 45 ~ "45 \u2264 p < 55  ",
    breacking_even < 45 ~ "0 \u2264 p < 45  "
  )) %>%
  ggplot(aes(factor(C), factor(P), z = breacking_even1, fill = breacking_even1, label = breacking_even1)) +
  geom_tile(color = "white", size = 0.5) +
  scale_fill_viridis(discrete = T, option = "E", begin = 0, end = 1, name = "Probability of not-offsetting costs (%)") +
  scale_color_gradient(high = "white", low = "white") +
  labs(x = "Fungicide + application cost (US$/ha)", y = "Wheat price (US$/ton) ", fill = "") +
  theme_minimal() +
  facet_wrap(~ fungicide, scales = "free", nrow=1) +
  theme(axis.title = element_text(size = 12, face = "bold"), 
        legend.justification = "center", 
        axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        strip.text.x = element_text(size = 14, face = "bold"), 
        strip.text.y = element_text(size = 14, face = "bold"), 
        panel.grid.minor = element_line(colour = "white"), 
        panel.grid.major = element_line(colour = "white"), 
        legend.position = "bottom")

ggsave("Figures/tetris.png", width = 9, height = 4, dpi = 300)
```






















